S2. Additional figures and table

### 2021-10-26 Manuscript/S2.Additional_outputs.Rmd
updated formatting

```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="Figure 1. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}

@@

`r print_table(var_importance_s1, caption = 'Table 1. Term importance at the end of Session 1.')`

`r print_table(var_importance_s2, caption = 'Table 2. Term importance at the end of Session 2.')`

@@

```{r hyperparameters, fig.width=17, fig.height=10, fig.cap="Figure 2. Score clusters and impact of single hyperparameters on engine performance. The performance is measured as Sensitivity x Efficiency. Each cluster is color coded. Mods: number of models in the ensemble; Quant: PrI quantiles for the uncertainty zone; Resamp: bootstrap resampling between models; Init: size of initial training set; Multi: oversampling rate of positive records"}

@@

`r print_table(grid_out_params, caption = 'Table 3. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.')`

>>>>

```{r posterior distributions, fig.width=10, fig.height=10, fig.cap="**Figure 1**. Mixture predictive distribution of the probability of a positive match, grouped by labelling status."}

@@

`r print_table(var_importance_s1, caption = '**Table 1**. Term importance at the end of Session 1.')`

`r print_table(var_importance_s2, caption = '**Table 2**. Term importance at the end of Session 2.')`

@@

```{r hyperparameters, fig.width=17, fig.height=10, fig.cap="**Figure 2**. Score clusters and impact of single hyperparameters on engine performance. The performance is measured as Sensitivity x Efficiency. Each cluster is color coded. Mods: number of models in the ensemble; Quant: PrI quantiles for the uncertainty zone; Resamp: bootstrap resampling between models; Init: size of initial training set; Multi: oversampling rate of positive records"}

@@

`r print_table(grid_out_params, caption = '**Table 3**. Hyperparameter clusters and best cluster subsets. For each cluster, the defining rules and mean Sens. x Eff. is shown, followed by the per-cluster best set results.')`
